% !TeX spellcheck = en_US
\documentclass[
10pt, A4, english,
draft = false,
twoside = false,
]{article}
\usepackage{applying-letter}

\begin{document}
	\onehalfspacing	
	%	Basic information	
	\setname{Huu Duc}{Nguyen}
	\setaddress{Aachen / Germany}
	\setmobile{(+49) 176 7685 2144}
	\setmail{huuduc.nguyen7295@gmail.com}
	\setlinkedin{https://www.linkedin.com/in/huu-duc-nguyen-689798197/}
	\setgithub{https://github.com/duken72}
	\setblog{https://duken72.github.io/}	
	%---------------------------------------------------------------------------------------
	%	Title + Contact
	%----------------------------------------------------------------------------------------
	\cvtitle{Cover Letter}
	%---------------------------------------------------------------------------------------
	%	Content
	%----------------------------------------------------------------------------------------
	{\fontsize{12}{0}\selectfont		
		\textbf{Dear Prof. Valada and Prof. Bödecker,}\\~\\
		In search of my teachers, I am writing to express my ambition in pursuing the \textbf{doctoral program in Robotics} at \textbf{University of Freiburg}. I believe that my experience and background make me a potential candidate.\\~\\
		In the past 9 years, the path I wish to follow gradually takes shape. During the years of my Bachelor's, there were times that I was lost in motivation, uncertain of who I am and who I should be. In those periods, to see the world, I have gone out of my home country, set foot to Europe, Japan, India and Singapore. The key take-aways were neither extra skills, meeting new people nor experiencing new cultures, but rather to see my own reflection in this world. After the journeys, I came back with the determination to finish whatever I have started.\\~\\		
		One of my strengths is the ability to utilize different learning resources. I came across this saying while listening to a podcast: “When the student is ready, the teacher will appear”. Through that podcast, I saw the changes I have made in the last couple of years. My teachers were not only those with academic professions, but also seniors, classmates, along with books, online blog posts, YouTube videos, etc. I would not only put my ego aside to learn from less experienced juniors, but also take pleasure in having discussion and explanation with others. On that account, at RWTH Aachen University, I am ranked in the top 5\% students, in terms of academic achievement, and have received the Best of Class Awards with scholarships twice.\\~\\		
		Practical skills are what I always try to hone. There are beauties in pieces of code, just as in poems or essays, and I do not mind rolling up my sleeves to get things worked. Despite finishing most given coding exercises from classes, with the determination to gain more experience with C++ and ROS, I chose the internship and master thesis at Robert Bosch GmbH. Even though having a topic out of my scope of interest, I have striven to learn as much as possible from my supportive supervisors and their talented colleagues.\\~\\
		For a long time I have been interested in robotics. After my Bachelor degree in Automatic Control, I believe the future of robotics would lie in the ability to integrate machines with visual knowledge and simulated experiences. With that interest, I continued with the robotic Master program, and now, in search of a relevant doctoral position.\\~\\
		There is an African proverb: “If you want to go fast, go alone. If you want to go far, go together”. With these words in mind, for the upcoming journey, I feel the utter need to find my teachers and colleagues. After looking into your papers and the team, I sense a great team dynamic, on-going research directions and alignment in our paths. I would love to know you guys more, and, perhaps, be a part of the team.\\~\\
		Thank you for your time and consideration.\\~\\		
		Best regards,\\
		Huu Duc Nguyen		
	}
\end{document}